Plots_manuscript_v0.3

### 2020-09-30 R/Plots_manuscript_v0.3.Rmd
Start comparisons of GWAS and QTL intervals with FT annotations

annos_dyln$top500SNPs_within50000bp %>%
  filter(CHR == "Chr05N" & region_start < 3000000 & region_start > 2000000) %>%
  select(`Gene ID`, `distance from gene`, `Arabidopsis thaliana homolog`, `Rice homolog`)
```
	Pavir.5NG109746 (18.7kb), 	AT1G49200 RING/U-box superfamily protein
		LOC_Os01g64620.1 highly expressed hypocotyl, silique
	Pavir.5NG109743 (22.5kb), 	AT2G22590 UDP-Glycosyltransferase superfamily pt.
	LOC_Os01g64540.1  highly expressed in mature flower petals
	Pavir.5NG109744 (17.9kb), 		AT2G35930 (PUB23) plant U-box 23
		LOC_Os01g64570.1 highly expressed in senescent leaf petiole; negative regulation of drought tolerance
	Pavir.5NG109745 (4.1kb)     AT2G28510 Dof-type zinc finger DNA-binding family protein  highly expressed in the carpel of the young flower & in seeds during germination day 1; promotes leaf senescence in arabidopsis
		LOC_Os01g64590.1

```{r}
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
set_v <- list(eight_sites = "eight_sites", tx_sites = "tx_sites", north_sites = "north_sites", single_sites = "!sites")
j = 1
annos_df <- read_csv(file = file.path(workingdir, "analysis", "gwas", "BLUPs",
                                    paste0(names(set_v)[j],     
                                           "_top_500_SNPs_above_FDR",
                                           "_closest_annotations.csv")))
for(j in seq_along(set_v)[-1]){
annos1 <- read_csv(file = file.path(workingdir, "analysis", "gwas", "BLUPs",
                                    paste0(names(set_v)[j],     
                                           "_top_500_SNPs_above_FDR",
                                           "_closest_annotations.csv")))
annos_df <- annos_df %>%
  full_join(annos1)
}

>>>>

annos_dyln$top500SNPs_within50000bp %>%
  filter(CHR == "Chr05N" & region_start < 3000000 & region_start > 2000000) %>%
  select(`Gene ID`, `distance from gene`, `Arabidopsis thaliana homolog`, `Rice homolog`)
```
	Pavir.5NG109746 (18.7kb), 	AT1G49200 RING/U-box superfamily protein
		LOC_Os01g64620.1 highly expressed hypocotyl, silique
	Pavir.5NG109743 (22.5kb), 	AT2G22590 UDP-Glycosyltransferase superfamily pt.
	LOC_Os01g64540.1  highly expressed in mature flower petals
	Pavir.5NG109744 (17.9kb), 		AT2G35930 (PUB23) plant U-box 23
		LOC_Os01g64570.1 highly expressed in senescent leaf petiole; negative regulation of drought tolerance
	Pavir.5NG109745 (4.1kb)     AT2G28510 Dof-type zinc finger DNA-binding family protein  highly expressed in the carpel of the young flower & in seeds during germination day 1; promotes leaf senescence in arabidopsis
		LOC_Os01g64590.1
## ---- #### ---- ####
```{r}
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
set_v <- list(eight_sites = "eight_sites", tx_sites = "tx_sites", north_sites = "north_sites", single_sites = "!sites")
j = 1
annos_df <- read_csv(file = file.path(workingdir, "analysis", "gwas", "BLUPs",
                                    paste0(names(set_v)[j],     
                                           "_top_500_SNPs_above_FDR",
                                           "_closest_annotations.csv")))
for(j in seq_along(set_v)[-1]){
annos1 <- read_csv(file = file.path(workingdir, "analysis", "gwas", "BLUPs",
                                    paste0(names(set_v)[j],     
                                           "_top_500_SNPs_above_FDR",
                                           "_closest_annotations.csv")))
annos_df <- annos_df %>%
  full_join(annos1)
}
